\section{Program transformations}


I'll be using the algorithm from wikipedia page on the topic $\lambda$-lifting.
I personally just find it easier to follow since
the steps are more clearly discribed compared to how it was described in our slides.
\\
\\
The algorithm is as following on the wikipedia page:
\begin{enumerate}
    \item Rename the functions so that each function has a unique name.
    \item Replace each free variable with an additional argument to the enclosing function, and pass that argument to every use of the function.
    \item Replace every local function definition that has no free variables with an identical global function.
    \item Repeat steps 2 and 3 until all free variables and local functions are eliminated.
\end{enumerate}
\newpage


\noindent \textbf{ ORIGINAL CODE SNIPPET:}
\begin{verbatim}
let rec bizarre b q =
    let mango z = b
    in
        if b then ( bizarre false mango )
            else ( mango 17 , q 17 );;

let dummy = function x -> false
let bongo = bizarre true dummy;;
\end{verbatim}

\noindent \textbf{STEP 1}, it is possible to skip step one of the algorithm, since all functions
are "unique" in the sence that there's no dublicates of functionnames that are
considered another function than the original.

\noindent \textbf{STEP 2)} the function named "mango" has a free variable b. So this variable has to be replaced 
and passed to every use of the function

I've chosen to replace variable name "b" with "mango\_b" and passed that argument to every other
use of the function "mango".

\begin{verbatim}
let rec bizarre b q =
    let mango z mango_b = mango_b
    in
        if b then ( bizarre false (mango z mango_b) )
            else ( mango 17 mango_b , q 17 );;

let dummy = function x -> false
let bongo = bizarre true dummy;;
\end{verbatim}

\noindent \textbf{STEP 3)} Is to lift the function(s) to a global scope.

REPLACING mango to mango'
\begin{verbatim}
let rec mango z mango_b = mango_b
and bizarre b q =
    if b then ( bizarre false (mango' z b))
        else ( mango' 17 b, q 17 );;

let dummy = function x -> false
let bongo = bizarre true dummy;;

mango' z mango_b = mango_b
\end{verbatim}
\newpage
\noindent \textbf{FINAL Program after lambda lifting}
\begin{verbatim}
let rec bizarre' b q =
    if b then ( bizarre false (mango' z b))
        else ( mango' 17 b, q 17 );;

let dummy = function x -> false
let bongo = bizarre true dummy;;
mango' z mango_b = mango_b
\end{verbatim}

\newpage